```{r echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.show = "hold",
  fig.align = "center",
  fig.width = 13.85,
  fig.height = 18.75,
  out.width = NULL
)
source("./R/mandala.R")
source("./R/sudoku.R")
source("./R/wordfinder.R")
source("./R/crossword.R")
source("./R/tictactoe.R")
source("./R/instruction.R")
try({
  sysfonts::font_add_google("Dancing Script")
})
showtext::showtext_auto()
options(book.font.type = "Dancing Script")
wordlist <- readLines("https://www.mit.edu/~ecprice/wordlist.10000")
debug <- FALSE
```

::: {.content-visible when-format="html"}
Welcome to this generative puzzle book! Created using the open-source programming language R, this book is completely [free](https://www.gnu.org/philosophy/free-sw.html)! And here's the best part: it never runs out! If you're craving more puzzles, just come back tomorrow. This book refreshes itself every day, generating 9 brand-new mandalas, 18 sudoku, 18 word finders, and 18 crossword puzzles for you to enjoy.

Click [here](https://koenderks.github.io/genigma/Genigma--Generative-Puzzle-Book.pdf) to download today's unique puzzle book!
:::

```{r echo = FALSE, message=FALSE}
mandalaseeds <- sample.int(.Machine$integer.max, 9)
names(mandalaseeds) <- 1:9
sudokuseeds <- sample.int(.Machine$integer.max, 18)
names(sudokuseeds) <- 1:18
wordfinderseeds <- sample.int(.Machine$integer.max, 18)
names(wordfinderseeds) <- 1:18
crosswordseeds <- sample.int(.Machine$integer.max, 18)
names(crosswordseeds) <- 1:18
```

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output()) {
  p1 <- mandala(type = "example")
  p2 <- .instruction("Mandala", "Color the mandala according to the example provided.")
  p3 <- sudoku(NULL, type = "example")
  p4 <- .instruction("Sudoku", "Fill in the blank squares so that each row, each column and each\n3-by-3 block contains all of the digits 1 to 9.")
  p5 <- wordfinder(NULL, wordlist, type = "example")
  p6 <- .instruction("Word Finder", "Locate and strike through all words in the puzzle. Words may\nappear vertically, horizontally, or diagonally and in any direction.\nNote that letters may be part of multiple words.")
  p7 <- crossword(NULL, wordlist, type = "example")
  p8 <- .instruction("Crossword", "Fill in the synonyms of the words in the list at their corresponding\npositions in the puzzle. Words only appear horizontally or vertically\nand in reading direction.")
  p9 <- tictactoe(type = "example")
  p10 <- .instruction("Tic Tac Toe", "Players take turns putting an 'X' or an 'O' mark in an empty square.\nThe first player to get 3 of their marks in a row is the winner. When\nall squares are full and there is no winner, the game ends in a tie.")
  gridExtra::grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, layout_matrix = matrix(c(
    1, 2, 2,
    4, 4, 3,
    5, 6, 6,
    8, 8, 7,
    9, 10, 10
  ), byrow = TRUE, nrow = 5, ncol = 3), top = grid::textGrob("— Instructions —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output()) {
  seed <- mandalaseeds[1]
  set.seed(seed)
  p1 <- mandala()
  set.seed(seed)
  p2 <- mandala(type = "solution")
  gridExtra::grid.arrange(p2, p1, layout_matrix = matrix(c(
    2, 2, 2, 2, 2,
    2, 2, 2, 2, 2,
    2, 2, 2, 2, 2,
    2, 2, 2, 1, 1,
    NA, NA, NA, 1, 1
  ), byrow = TRUE, nrow = 5, ncol = 5), top = grid::textGrob("— Mandala —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output()) {
  set.seed(sudokuseeds[1])
  sudoku(sudokuseeds[1])
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output()) {
  set.seed(wordfinderseeds[1])
  wordfinder(wordfinderseeds[1], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output()) {
  set.seed(crosswordseeds[1])
  crossword(crosswordseeds[1], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(sudokuseeds[2])
  sudoku(sudokuseeds[2])
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(wordfinderseeds[2])
  wordfinder(wordfinderseeds[2], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(crosswordseeds[2])
  crossword(crosswordseeds[2], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE, fig.height = 16}
if (!knitr::is_html_output()) {
  plotList <- list()
  for (i in 1:12) {
    plotList[[length(plotList) + 1]] <- tictactoe()
  }
  gridExtra::grid.arrange(grobs = plotList, layout_matrix = matrix(1:12, byrow = TRUE, nrow = 4, ncol = 3), top = grid::textGrob("— Tic Tac Toe —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  seed <- mandalaseeds[2]
  set.seed(seed)
  p1 <- mandala()
  set.seed(seed)
  p2 <- mandala(type = "solution")
  gridExtra::grid.arrange(p2, p1, layout_matrix = matrix(c(
    2, 2, 2, 2, 2,
    2, 2, 2, 2, 2,
    2, 2, 2, 2, 2,
    2, 2, 2, 1, 1,
    NA, NA, NA, 1, 1
  ), byrow = TRUE, nrow = 5, ncol = 5), top = grid::textGrob("— Mandala —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(sudokuseeds[3])
  sudoku(sudokuseeds[3])
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(wordfinderseeds[3])
  wordfinder(wordfinderseeds[3], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(crosswordseeds[3])
  crossword(crosswordseeds[3], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(sudokuseeds[4])
  sudoku(sudokuseeds[4])
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(wordfinderseeds[4])
  wordfinder(wordfinderseeds[4], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(crosswordseeds[4])
  crossword(crosswordseeds[4], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  seed <- mandalaseeds[3]
  set.seed(seed)
  p1 <- mandala()
  set.seed(seed)
  p2 <- mandala(type = "solution")
  gridExtra::grid.arrange(p2, p1, layout_matrix = matrix(c(
    2, 2, 2, 2, 2,
    2, 2, 2, 2, 2,
    2, 2, 2, 2, 2,
    2, 2, 2, 1, 1,
    NA, NA, NA, 1, 1
  ), byrow = TRUE, nrow = 5, ncol = 5), top = grid::textGrob("— Mandala —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(sudokuseeds[5])
  sudoku(sudokuseeds[5])
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(wordfinderseeds[5])
  wordfinder(wordfinderseeds[5], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(crosswordseeds[5])
  crossword(crosswordseeds[5], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(sudokuseeds[6])
  sudoku(sudokuseeds[6])
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(wordfinderseeds[6])
  wordfinder(wordfinderseeds[6], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(crosswordseeds[6])
  crossword(crosswordseeds[6], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE, fig.height = 16}
if (!knitr::is_html_output() && !debug) {
  plotList <- list()
  for (i in 1:12) {
    plotList[[length(plotList) + 1]] <- tictactoe()
  }
  gridExtra::grid.arrange(grobs = plotList, layout_matrix = matrix(1:12, byrow = TRUE, nrow = 4, ncol = 3), top = grid::textGrob("— Tic Tac Toe —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  seed <- mandalaseeds[4]
  set.seed(seed)
  p1 <- mandala()
  set.seed(seed)
  p2 <- mandala(type = "solution")
  gridExtra::grid.arrange(p2, p1, layout_matrix = matrix(c(
    2, 2, 2, 2, 2,
    2, 2, 2, 2, 2,
    2, 2, 2, 2, 2,
    2, 2, 2, 1, 1,
    NA, NA, NA, 1, 1
  ), byrow = TRUE, nrow = 5, ncol = 5), top = grid::textGrob("— Mandala —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(sudokuseeds[7])
  sudoku(sudokuseeds[7])
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(wordfinderseeds[7])
  wordfinder(wordfinderseeds[7], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(crosswordseeds[7])
  crossword(crosswordseeds[7], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(sudokuseeds[8])
  sudoku(sudokuseeds[8])
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(wordfinderseeds[8])
  wordfinder(wordfinderseeds[8], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(crosswordseeds[8])
  crossword(crosswordseeds[8], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  seed <- mandalaseeds[5]
  set.seed(seed)
  p1 <- mandala()
  set.seed(seed)
  p2 <- mandala(type = "solution")
  gridExtra::grid.arrange(p2, p1, layout_matrix = matrix(c(
    2, 2, 2, 2, 2,
    2, 2, 2, 2, 2,
    2, 2, 2, 2, 2,
    2, 2, 2, 1, 1,
    NA, NA, NA, 1, 1
  ), byrow = TRUE, nrow = 5, ncol = 5), top = grid::textGrob("— Mandala —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(sudokuseeds[9])
  sudoku(sudokuseeds[9])
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(wordfinderseeds[9])
  wordfinder(wordfinderseeds[9], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(crosswordseeds[9])
  crossword(crosswordseeds[9], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(sudokuseeds[10])
  sudoku(sudokuseeds[10])
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(wordfinderseeds[10])
  wordfinder(wordfinderseeds[10], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(crosswordseeds[10])
  crossword(crosswordseeds[10], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE, fig.height = 16}
if (!knitr::is_html_output() && !debug) {
  plotList <- list()
  for (i in 1:12) {
    plotList[[length(plotList) + 1]] <- tictactoe()
  }
  gridExtra::grid.arrange(grobs = plotList, layout_matrix = matrix(1:12, byrow = TRUE, nrow = 4, ncol = 3), top = grid::textGrob("— Tic Tac Toe —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  seed <- mandalaseeds[6]
  set.seed(seed)
  p1 <- mandala()
  set.seed(seed)
  p2 <- mandala(type = "solution")
  gridExtra::grid.arrange(p2, p1, layout_matrix = matrix(c(
    2, 2, 2, 2, 2,
    2, 2, 2, 2, 2,
    2, 2, 2, 2, 2,
    2, 2, 2, 1, 1,
    NA, NA, NA, 1, 1
  ), byrow = TRUE, nrow = 5, ncol = 5), top = grid::textGrob("— Mandala —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(sudokuseeds[11])
  sudoku(sudokuseeds[11])
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(wordfinderseeds[11])
  wordfinder(wordfinderseeds[11], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(crosswordseeds[11])
  crossword(crosswordseeds[11], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(sudokuseeds[12])
  sudoku(sudokuseeds[12])
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(wordfinderseeds[12])
  wordfinder(wordfinderseeds[12], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(crosswordseeds[12])
  crossword(crosswordseeds[12], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  seed <- mandalaseeds[7]
  set.seed(seed)
  p1 <- mandala()
  set.seed(seed)
  p2 <- mandala(type = "solution")
  gridExtra::grid.arrange(p2, p1, layout_matrix = matrix(c(
    2, 2, 2, 2, 2,
    2, 2, 2, 2, 2,
    2, 2, 2, 2, 2,
    2, 2, 2, 1, 1,
    NA, NA, NA, 1, 1
  ), byrow = TRUE, nrow = 5, ncol = 5), top = grid::textGrob("— Mandala —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(sudokuseeds[13])
  sudoku(sudokuseeds[13])
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(wordfinderseeds[13])
  wordfinder(wordfinderseeds[13], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(crosswordseeds[13])
  crossword(crosswordseeds[13], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(sudokuseeds[14])
  sudoku(sudokuseeds[14])
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(wordfinderseeds[14])
  wordfinder(wordfinderseeds[14], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(crosswordseeds[14])
  crossword(crosswordseeds[14], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE, fig.height = 16}
if (!knitr::is_html_output() && !debug) {
  plotList <- list()
  for (i in 1:12) {
    plotList[[length(plotList) + 1]] <- tictactoe()
  }
  gridExtra::grid.arrange(grobs = plotList, layout_matrix = matrix(1:12, byrow = TRUE, nrow = 4, ncol = 3), top = grid::textGrob("— Tic Tac Toe —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  seed <- mandalaseeds[8]
  set.seed(seed)
  p1 <- mandala()
  set.seed(seed)
  p2 <- mandala(type = "solution")
  gridExtra::grid.arrange(p2, p1, layout_matrix = matrix(c(
    2, 2, 2, 2, 2,
    2, 2, 2, 2, 2,
    2, 2, 2, 2, 2,
    2, 2, 2, 1, 1,
    NA, NA, NA, 1, 1
  ), byrow = TRUE, nrow = 5, ncol = 5), top = grid::textGrob("— Mandala —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(sudokuseeds[15])
  sudoku(sudokuseeds[15])
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(wordfinderseeds[15])
  wordfinder(wordfinderseeds[15], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(crosswordseeds[15])
  crossword(crosswordseeds[15], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(sudokuseeds[16])
  sudoku(sudokuseeds[16])
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(wordfinderseeds[16])
  wordfinder(wordfinderseeds[16], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(crosswordseeds[16])
  crossword(crosswordseeds[16], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  seed <- mandalaseeds[9]
  set.seed(seed)
  p1 <- mandala()
  set.seed(seed)
  p2 <- mandala(type = "solution")
  gridExtra::grid.arrange(p2, p1, layout_matrix = matrix(c(
    2, 2, 2, 2, 2,
    2, 2, 2, 2, 2,
    2, 2, 2, 2, 2,
    2, 2, 2, 1, 1,
    NA, NA, NA, 1, 1
  ), byrow = TRUE, nrow = 5, ncol = 5), top = grid::textGrob("— Mandala —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(sudokuseeds[17])
  sudoku(sudokuseeds[17])
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(wordfinderseeds[17])
  wordfinder(wordfinderseeds[17], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(crosswordseeds[17])
  crossword(crosswordseeds[17], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(sudokuseeds[18])
  sudoku(sudokuseeds[18])
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(wordfinderseeds[18])
  wordfinder(wordfinderseeds[18], wordlist)
}
```
\clearpage

```{r echo = FALSE, message=FALSE}
if (!knitr::is_html_output() && !debug) {
  set.seed(crosswordseeds[18])
  crossword(crosswordseeds[18], wordlist)
}
```
\clearpage

<!-- Answers -->
```{r echo = FALSE, message=FALSE, fig.height = 16}
if (!knitr::is_html_output()) {
  plotList <- list()
  for (i in 1:9) {
    set.seed(sudokuseeds[i])
    plotList[[length(plotList) + 1]] <- sudoku(sudokuseeds[i], type = "solution")
  }
  gridExtra::grid.arrange(grobs = plotList, layout_matrix = matrix(1:9, byrow = TRUE, nrow = 3, ncol = 3), top = grid::textGrob("— Sudoku ~ Solutions —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE, fig.height = 16}
if (!knitr::is_html_output() && !debug) {
  plotList <- list()
  for (i in 10:18) {
    set.seed(sudokuseeds[i])
    plotList[[length(plotList) + 1]] <- sudoku(sudokuseeds[i], type = "solution")
  }
  gridExtra::grid.arrange(grobs = plotList, layout_matrix = matrix(1:9, byrow = TRUE, nrow = 3, ncol = 3), top = grid::textGrob("— Sudoku ~ Solutions —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE, fig.height = 16}
if (!knitr::is_html_output()) {
  plotList <- list()
  for (i in 1:9) {
    set.seed(wordfinderseeds[i])
    plotList[[length(plotList) + 1]] <- wordfinder(wordfinderseeds[i], wordlist, type = "solution")
  }
  gridExtra::grid.arrange(grobs = plotList, layout_matrix = matrix(1:9, byrow = TRUE, nrow = 3, ncol = 3), top = grid::textGrob("— Word Finder ~ Solutions —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE, fig.height = 16}
if (!knitr::is_html_output() && !debug) {
  plotList <- list()
  for (i in 10:18) {
    set.seed(wordfinderseeds[i])
    plotList[[length(plotList) + 1]] <- wordfinder(wordfinderseeds[i], wordlist, type = "solution")
  }
  gridExtra::grid.arrange(grobs = plotList, layout_matrix = matrix(1:9, byrow = TRUE, nrow = 3, ncol = 3), top = grid::textGrob("— Word Finder ~ Solutions —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE, fig.height = 16}
if (!knitr::is_html_output()) {
  plotList <- list()
  for (i in 1:9) {
    set.seed(crosswordseeds[i])
    plotList[[length(plotList) + 1]] <- crossword(crosswordseeds[i], wordlist, type = "solution")
  }
  gridExtra::grid.arrange(grobs = plotList, layout_matrix = matrix(1:9, byrow = TRUE, nrow = 3, ncol = 3), top = grid::textGrob("— Crossword ~ Solutions —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage

```{r echo = FALSE, message=FALSE, fig.height = 16}
if (!knitr::is_html_output() && !debug) {
  plotList <- list()
  for (i in 10:18) {
    set.seed(crosswordseeds[i])
    plotList[[length(plotList) + 1]] <- crossword(crosswordseeds[i], wordlist, type = "solution")
  }
  gridExtra::grid.arrange(grobs = plotList, layout_matrix = matrix(1:9, byrow = TRUE, nrow = 3, ncol = 3), top = grid::textGrob("— Crossword ~ Solutions —", gp = grid::gpar(fontsize = 75, fontfamily = getOption("book.font.type", "sans"), fontface = "bold")))
}
```
\clearpage
